\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2020-07-27 sections/acknowledgments.tex
Updates to draft
Updates from Overleaf

\section*{Acknowledgments}

  We are grateful for ...

>>>>

% TODO: Update this section
\section*{Acknowledgments}

We are grateful to members of the Segrè lab for helpful discussions and for feedback on the manuscript. This work was partially funded by grants from the NIH (T32GM100842, 5R01DE024468, R01GM121950 and NIA UH2AG064704), NSFOCE-BSF grant 1635070, the Human Frontiers Science Program (RGP0020/2016), and the Boston University Interdisciplinary Biomedical Research Office. [DANIEL, KIRILL: MISSING GRANTS???]

\section*{Contributions}

### 2020-07-27 sections/methods.tex
Updates from Overleaf

  \subsection*{Code and Data Availability}
  pipeline: \href{https://github.com/segrelab/MiCoNE}{https://github.com/segrelab/MiCoNE} \\
  data and scripts related to the paper: \href{}{}

>>>>

  \subsection*{Code and Data Availability}
  pipeline: \href{https://github.com/segrelab/MiCoNE}{https://github.com/segrelab/MiCoNE} \\
  data and scripts related to the paper: \href{https://github.com/segrelab/MiCoNE-pipeline-paper}{https://github.com/segrelab/MiCoNE-pipeline-paper}
